Enter our title here

### 2017-09-06 manuscript.tex
added image
Added to 'how-to' section (tips/explanation of exercise headers)

Questions: 
1) should i add more about how it can be used in a flipped classroom?

@@

With this increased use of R in classrooms, there is a need for an effective way to get students familiar with R \cite{Baumer2014}. While R
software provides users with extraordinary abilities there is no doubt a steep learning curve. To facilitate this transition
to R programming, popular interactive teaching technologies have been created including Swirl (need to cite this?), LearnR
and TryR. These tools
allow students to work through coding problems while recieving immediate feedback in and out of the classroom. Swirl is an
open source R software package that allows students to learn R programing in their R console. This interactive learning tool
contains several pre-existing lessons but what makes Swirl so popular is its versitality; educators can create their own
lesson (or tailor a pre-existing one) to fit their curriculum and assign it to students \cite{Carchedi2014}.
While swirl can be linked to a Massive Open Online Courses (MOOCs) like Coursera through API, this is not avaiblable for the classroom
learning management systems (LMS).

@@

DataCamp has the same reproducable capabilities as Swirl but is a web-based application; educators can
create their own courses that coincide with their lessons and students can access the course without having to install R.
Courses are available through the DataCamp website and students can access the lesson through their web-browser on a laptop,
tablet or moble device, making the courses accessable to anyone with an internet connection. 
The DataCamp website offers pre-existing free community courses and specialized 'Premium' classes that you need to purchase. 
However, when used for academic purposes the premium DataCamp content is also free of charge.. (i'll come back to this).
Any college educator can create a classroom group on the DataCamp website, add student's to the group, assign pre-existing 
'community' courses and assign a course that they've created for the particular class.

@@

\subsection{Creating a DataCamp Course}
To create a course on DataCamp you will first need to create a DataCamp account by visiting \url{www.datacamp.com/teach} and
also a GitHub account. The simplest way to begin building the course is to use the templete course files from the 'Create
DataCamp Course' dialog. This will automatically create a GitHub repository that is linked to DataCamp; any changes that are
make through DataCamp will update the GitHub repository and visa versa. Every DataCamp course is linked through GitHub version control,
allowing statistics educators to easily collaborate and reproduce code. To add collaborators to the course, go to the course repository
on GitHub and under 'Settings' you can select the 'Collabroators' tab and enter the usernames of people you want to collaborate with.

@@

The submission correctness testing code (or SCT) is the backbone for DataCamps' interactive nature. If a student submits an incorrect answer, they will 
receive immediate feedback on what they are doing wrong and the system will guide them to the right answer. Instructors can use the default feedback
that DataCamp automatically generates or write their own custom messages. The default feedback is meaningful and specific; most of the time custom 
messages are not necessary unless there is a common problem that student are struggling with in which more unique feedback is necessary. 
DataCamp provides a helpful R package called 'testwhat' which acts as a guide to writing and using SCTs (this can be accessed on DataCamp's GitHub 
repository: 'datacamp/testwhat'). 
'testwhat' contains functions that can test different types of problems including loops, object definitions, printed output, functions, ect 
(datacamp website), this submission correctness testing code compares the ideal answer (from the solution) to the students answer. Different
arguements can be added to the test functions to alter the testing process and automatic feedback.

%add an example of a test_function sct

@@

%add example of a normal coding exercise

\begin{figure}
  \includegrpahics[width = \linewidth] {preview.jpg}
\end{figure}

The 'MultipleChoiceExercise', as you would expect, contains a question and a list of various answers. Instructors write the questions in the 'lesson'
portion of the exercise and offer solutions in the 'Insruction' section. Like the 'normal' coding exercises, the lesson, instructions, pre-exercise 
code and SCTs have to be specified but sample and solution code do not. DataCamp offers two types of multiple choice questions, simple and regular. 
The simple multiple choice exercises are used for questions that do not require the R console or any R output. Regular multiple choice exercises 
allow instructors to pre-program objects or plots that the student needs to access to answer the question. Both types of multiple choice exercises 
are straightforward to write can act as quick checks for understanding throughout the chapter.

%add example of regular multiple choice exercise

@@

@@

%Use this for final submission
%\bibliographystyle{ECA_jasa}
\bibliographystyle{Chicago}
\bibliography{library}

>>>>

Questions:

1) should i add more about how it can be used in a flipped classroom?

2) how to get side by side pictures (for the teach editor code vs. preview)?

3) also, what is the best way to add pictures? They are not inserted in the pdf where i have the code

4) what are the bottom comments about the citations?

@@

With this increased use of R in classrooms, there is a need for an effective way to get students familiar with statistical software
\cite{Baumer2014}. While Rsoftware provides users with extraordinary abilities there is no doubt a steep learning curve. To facilitate
this transition to R programming, popular interactive teaching technologies have been created including Swirl (need to cite this?), LearnR
and TryR. 
These tools allow students to work through coding problems while recieving immediate feedback in and out of the classroom. Swirl is an
open source R software package that allows students to learn R programing in their R console. This interactive learning tool
contains several pre-existing lessons but what makes Swirl so popular is its versitality; educators can create their own
lesson (or tailor a pre-existing one) to fit their curriculum and assign it to students \cite{Carchedi2014}.
While swirl can be linked to a Massive Open Online Courses (MOOCs) like Coursera through API, integration of learning management 
systems (LMS) is not available for the classroom.

@@

DataCamp has the same reproducable capabilities as Swirl but is a web-based application; educators can
create their own courses that coincide with their lessons and students can access the course without having to install R.
Courses are available through the DataCamp website and students can access the lesson through their web-browser on a laptop,
tablet or moble device, making the courses accessable to anyone with an internet connection. 
The DataCamp website offers pre-existing free community courses as well as specialized 'Premium' classes that you need to purchase. 
However, when used for academic purposes the premium DataCamp content is also free of charge.. (i'll come back to this).
Any college educator can create a classroom group on the DataCamp website, add student's to the group, assign pre-existing 
'community' courses or assign a course that they've created for the particular class.

@@

\subsection{Creating a DataCamp Course}
To build a course on DataCamp you will first need to create a DataCamp account by visiting \url{www.datacamp.com/teach} and
a GitHub account \url{https://github.com}. The simplest way to begin building the course is to use the templete course files from the 'Create
DataCamp Course' dialog. This will automatically create a GitHub repository that is linked to DataCamp; any changes that are
make through DataCamp will update the GitHub repository and visa versa. Every DataCamp course is linked through GitHub version control,
allowing statistics educators to easily collaborate and reproduce code. To add collaborators to the course, go to the course repository
on GitHub and under 'Settings' you can select the 'Collabroators' tab and enter the usernames of people you want to collaborate with.

@@

\begin{figure}[h]
  \includegraphics[scale = 0.2] {edit.jpg}
\end{figure}

\begin{figure}[h]
  \includegraphics[scale = 0.19] {preview.jpg}
\end{figure}

Whenever a new exercise is added, DataCamp automatically produces the top line in the editor. The header specifies the type
of exercise (type), language (lang), available points (xp), skills learned (skills) and a 'key'. The key acts as a unique
identifier for that exercise, allowing you to modify the content without losing any student data. Currenly, DataCamp offers
eight different skills which are defined by numbers 1-8. The skills and their corresponding numbers can be found in the DataCamp
documentation \url{https://www.datacamp.com/teach/documentation#tab_gamification}. 
In the above exercise code, the 'type' is Normal, the language is R, the available points is 100 and the skills learned is 1 (which 
corresponds to *R Programming*. DataCamp assigns 100 points to normal coding exercises but this value can be modified depending on
difficulty level. After students have completed the exercise, they can check their personal profile to see how many points they earned.

@@

The submission correctness testing code (or SCT) is the backbone for DataCamps' interactive nature. If a student submits an incorrect answer, they will 
receive immediate feedback on what they are doing wrong and the system will guide them to the right answer. Instructors can use the default feedback
that DataCamp automatically generates or write their own custom messages. The default feedback is meaningful and specific; most of the time custom 
messages are not necessary unless there is a common problem that student are struggling with in which more unique feedback is necessary. 
DataCamp provides a helpful R package called 'testwhat' which acts as a guide to writing and using SCTs (this can be accessed on DataCamp's GitHub 
repository: \url{https://github.com/datacamp/testwhat/wiki}. 
'testwhat' contains functions that can test different types of problems including loops, object definitions, printed output, functions, ect.
The submission correctness testing code compares the ideal answer (from the solution) to the students answer. Different
arguements can be added to the test functions to alter the testing process and automatic feedback. (**do I cite datacamp website here?**)

%add an example of a test_function sct.... maybe plot

The 'MultipleChoiceExercise', as you would expect, contains a question and a list of various answers. Instructors write the questions in the 'lesson'
portion of the exercise and offer solutions in the 'Insructions' section. Similar to the 'normal' coding exercises, the lesson, instructions, pre-exercise 
code and SCTs have to be specified but sample and solution code do not. DataCamp offers two types of multiple choice questions: simple and regular. 
The simple multiple choice exercises are used for questions that do not require the R console or any R output. Regular multiple choice exercises 
allow instructors to pre-program objects or plots that the student needs to access to answer the question. Both types of multiple choice exercises 
are straightforward to write can act as quick checks for understanding throughout the chapter.

%add example of regular multiple choice exercise --> use Quick check 2 from lab 8

@@

All DataCamp courses will have a course badge and most will use data sets and R packages. Information on how to add data sets and images
can be found in DataCamps 'Teach' documentation \url{https://www.datacamp.com/teach/documentation} under the 'Upload Assets' tab. However,
there is currently no information on DataCamp about integrating R packages. To use R packages in a course, you will need to create a new file
in the GitHub course repository named 'requirements.r'. The file should contain: $devtools::install_version$, package name and version for every
package you use in the DataCamp course. For example, following code will add the 'ggplot2' and 'mosaic' packages to the repository.

$$devtools::install_version("ggplot2", "2.2.0")$$
$$devtools::install_version("mosaic", "0.14.4")$$

In order for DataCamp to recognize this new file, you will need to add $$from: r-base-prod:27$$ to the course.yml file.

**How do I override the subscripts for devtools?**

@@

%Use this for final submission
%\bibliographystyle{ECA_jasa}
\bibliographystyle{Chicago}
\bibliography{TISE-DataCamp(Private Group)}
% before it was 'library' so I thought if I changed it to the new bib file it would work but it doesn't :(
